PLUNGER: Reproducing FLUSH+RELOAD: A High-Resolution, Low-Latency Side Channel Attack On GnuPG

### 2014-12-17 paper/paper.tex
Minor LaTeX cleanup
Everything fits under textwidth=80.

A possible future application of the \flushreload{} technique would be to
perform this attack across virtual machines. That is, using the attack to steal
data from one virtual machine whilst running the attack on another. Cross-VM
attacks are described in further detail by Apecechea et al.
\cite{cryptoeprint:2014:248}; the basic principle behind the attack would be to
detect and spy upon a victim, i.e. a user on another VM, running GnuPG (or some
equivalent cryptographic process) and steal the keys used in the process. Such
an attack clearly has its appeal: it would expose a major vulnerability in
virtual machines, which are used in countless modern software applications.

>>>>

A possible future application of the \flushreload{} technique would be to
perform this attack across virtual machines. That is, using the attack to steal
data from one virtual machine whilst running the attack on another. Cross-VM
attacks are described in further detail by Apecechea et al.
\cite{cryptoeprint:2014:248}; the basic principle behind the attack would be to
detect and spy upon a victim, i.e.\ a user on another VM, running GnuPG (or some
equivalent cryptographic process) and steal the keys used in the process. Such
an attack clearly has its appeal: it would expose a major vulnerability in
virtual machines, which are used in countless modern software applications.
